saycam full dataset -- preprocessing

### 2020-05-06 preprocessing/4_preprocess_datasets.Rmd
organizing repo: ordering steps more clearly

gold_sample <- ketan_gold_out %>%
  select(-vid_name) %>%
  rename(vid_name = vid_name_short) %>% 
  mutate(vid_name = as.factor(vid_name))

>>>>

gold_sample <- ketan_gold_out %>%
  select(-vid_name) %>%
  rename(vid_name = vid_name_short) %>% 
  mutate(vid_name = as.factor(vid_name)) %<%
  filter(!vid_name %in% to_exclude$vid_name)
